Realizing temporal graphs from fastest travel times

### 2023-02-06 ICALP23-RealizingTemporalGraphs.tex
Changes from Monday 6th Feb

Graph realization problems are fundamental graph-algorithmic questions where the objective is to (re)construct a graph, 
given some constraints on some of its graph attributes. Among the most well studied such parameters for graph reconstruction 
are the vertex degrees~\cite{}, distances~\cite{}, eccentricities~\cite{}, connectivity~\cite{}, etc. 
The motivation for network realization problems stems from both ``verification'' applications where we attempt to reconstruct an existing network of unknown structure based on the outcomes of experimental measurements, and engineering applications related to network design~\cite{.....}.

@@

Let $G=(V,E)$ and $\Delta\in \mathbb{N}$, and let $\lambda: E \rightarrow \{1,2,\ldots,\Delta\}$ be an edge-labeling function that assigns to every edge of $G$ one of the labels from $\{1,\ldots,\Delta\}$. 
Then we denote by $(G,\lambda,\Delta)$ the \emph{$\Delta$-periodic temporal graph} $(G,\lambda_{\Delta})$, where for every edge $e\in E$ we have $\lambda_{\Delta}(e)=\{i\Delta + x : i\geq 0, x\in \lambda(e)\}$. 
In this case we call $\lambda$ a \emph{$\Delta$-periodic labeling} of $G$.
When it is clear from the context, we drop $\Delta$ form the notation and say that $(G,\lambda)$ is $\Delta$ periodic temporal graph.

@@

	When considering the problem of finding shortest paths among vertices, one relies heavily on the optimal substructure of the problem,
	which implies that if a shortest path $P$ from vertex $u$ to $v$ traverses the vertex $w$,
	then the shortest path from $u$ to $w$ is a subpath of $P$.
	After studying the problem of fastest temporal paths (\ie temporal paths of smallest duration),
	one can see that this property does not carry over.
	For an example see~\cref{fig:ftpExample}.
	Which makes all the standard intuition and work with these kind of paths, much harder.

@@

	\draw[red]
	(v1) edge[diredge2] [out=85,in=95,distance=2.1cm] node[pos=0.3,yshift=2,label=above:$P_{u,w}$] {} (v3) ;
\end{tikzpicture}
	\caption{An example of a temporal graph, where the fastest temporal path $P_{u,v}$ (in blue) from $u$ to $v$ is of duration $7$,
		while the fastest temporal path $P_{u,w}$ (in red) from $u$ to a vertex $w$ that is on a path $P_{u,v}$ is of duration $1$ and is not a subpath of $P_{u,v}$.		
		\label{fig:ftpExample}}
	\end{figure}

@@

    \subparagraph{Verification Gadget.} For each color $i$, we introduce the following vertices. What we describe in the following will be used as a \emph{verification gadget for color $i$}.
    \begin{itemize}
        \item We have one vertex $y^i$ and $k+1$ vertices $v^i_\ell$ for $0\le \ell\le k$.
        \item For every $\ell\in[m]$ and every $j\in[k]\setminus\{i\}$ we have $5n$ vertices $a^{i,j,\ell}_1,a^{i,j,\ell}_2,\ldots,a^{i,j,\ell}_{5n}$ and $5n$ vertices $b^{i,j,\ell}_1,b^{i,j,\ell}_2,\ldots,b^{i,j,\ell}_{5n}$.
        \item We have a set $\hat{U}_i$ of $13n$ vertices $\hat{u}^i_1,\hat{u}^i_2,\ldots,\hat{u}^i_{13n}$.
    \end{itemize}
    We add the following edges. We add edge $\{y^i,v^i_0\}$.
    %For every $j\in[k]\setminus\{i,i+1\}$ and every $\ell\in[m]$ we add edge $\{v^i_{j-1},\hat{u}^{i,j,\ell}_1\}$. For every $\ell\in[m]$ we add edge $\{\hat{u}^i_{n+3},\hat{u}^{i,i+1,\ell}_1\}$.
    For every $\ell\in[m]$, every $j\in[k]\setminus\{i\}$, and every $\ell'\in[5n-1]$ we add edge $\{a^{i,j,\ell}_{\ell'},a^{i,j,\ell}_{\ell'+1}\}$ and we add edge $\{b^{i,j,\ell}_{\ell'},b^{i,j,\ell}_{\ell'+1}\}$.
    %Assume $1\neq i \neq k$. We describe the two cases $i=1$ and $i=k$ afterwards. 
    %If $i\neq 1$, let $e_\ell\in F_{1,i}$ let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$. Then we add edge $\{v^i_0,u^\ell_{\ell'}\}$ between $v^i_0$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget of color combination $1,i$.

@@

    We add edge $\{v^i_{i-1},\hat{u}^i_1\}$ and for all $\ell\in[11n-1]$ we add edge $\{\hat{u}^i_\ell,\hat{u}^i_{\ell+1}\}$. Furthermore, we add edge $\{\hat{u}^i_{13n},v^i_i\}$. 
    %Let $e_\ell^{i,i+1}\in F_{i,i+1}$ and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell^{i,i+1}$. If $i\neq 1\neq k$, then we add edge $\{\hat{u}^i_{n+3},a^{i,i+1,\ell}_{1}\}$ and edge $\{a^{i,i+1,\ell}_{5n},u^\ell_{n+\ell'-1}\}$ between $a^{i,i+1,\ell}_{5n}$ and the vertex $u^\ell_{n+\ell'-1}$ of the edge selection gadget of color combination $i,i+1$. If $i=1$, then we add edge $\{v^i_0,a^{i,i+1,\ell}_{1}\}$ and edge $\{a^{i,i+1,\ell}_{5n},u^\ell_{n+\ell'-1}\}$ between $a^{i,i+1,\ell}_{5n}$ and the vertex $u^\ell_{n+\ell'-1}$ of the edge selection gadget of color combination $i,i+1$.
%Furthermore, we add edge $\{v_{i+1}^i,b^{i,i+1,\ell}_{1}\}$ and edge $\{b^{i,i+1,\ell}_{5n},u^\ell_{\ell'}\}$ between $b^{i,i+1,\ell}_{5n}$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget of color combination $i,i+1$.

@@

Next, consider the validation gadget for color $i$. 
%Let $1\le j<i$, let $e_\ell\in F_{j,i}$, and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$. We set the following.
%\begin{itemize}
    %\item We set $d(v^i_{j-1},w^i_{\ell'+1})=3$.
    %\item We set $d(w^i_{\ell'},v^i_{j})=3$.
%\end{itemize}
%
For all $0\le j<j'<i$ and all $i\le j<j'\le k$ we set the following.
\begin{itemize}
    \item We set $d(v^i_j,v^i_{j'})=(20n+2)(j'-j)-1$.
\end{itemize}
%The next cases are only relevant if $1\neq i \neq k$. 
%For all $0\le j<i$ %and $\ell\in[n+3]$ we set the following.
%\begin{itemize}
%    \item We set $d(v^i_j,\hat{u}^i_{n+3})=(20n+2)(i-j-1)+2n+5$.
%\end{itemize}
%For all $\ell,\ell'\in[n+3]$ with $\ell<\ell'$ we set the following.
%\begin{itemize}
%    \item We set $d(\hat{u}^i_{\ell},\hat{u}^i_{\ell'})=2(\ell'-\ell)-1$.
%\end{itemize}
For all $0\le j<i$ and all $i\le j'\le k$ we set the following.
\begin{itemize}
    \item We set $d(v^i_j,v^i_{j'})=(20n+2)(j'-j)+6n-1$.
\end{itemize}
%For all 
%$\ell\in[n+3]$ and 
%$i<j\le k$ we set the following.
%\begin{itemize}
%    \item We set $d(\hat{u}^i_{n+3},v^i_j)=(20n+2)(j-i)-1$.
%\end{itemize}

Finally, we consider the alignment gadget. Let $x_1$ belong to the edge selection gadget of color combination $i,j$ and let $w\in \hat{W}$ denote the neighbor of $x_1$ in the alignment gadget. Let $\hat{v}_1$ and $\hat{v}_2$ belong to the first connector gadget of the edge selection gadget for color combination $i,j$. Let $\hat{V}$ contain all vertices $\hat{v}_1$ and $\hat{v}_2$ belonging to the other connector gadgets (different from the first one of the edge selection gadget for color combination $i,j$). 
\begin{itemize}
    \item We set $d(w^\star,x_1)=(20n+2)(i+j)$.
    \item We set $d(w^\star,\hat{v}_1)=n^9$, $d(w,\hat{v}_2)=n^9$, $d(w,\hat{v}_1)=n^9-(20n+2)(i+j)+1$, and $d(w,\hat{v}_2)=n^9-(20n+2)(i+j)+1$.
    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus (X_{i,j}\cup \{v_{i,j}^{\star\star}\})$ we set $d(w^\star,v)=n^9+2$ and $d(w,v)=n^9-(20n+2)(i+j)+3$.
\end{itemize}

@@

\begin{claim}\label{claim:4}
    For all $1\le i<j\le k$ and $\ell\in[m]$ we have that $\lambda(\{x_\ell,v_{i,j}^{\star}\})=(i+j)\cdot (2n\ell^2 +18n+2)$, where $x_\ell$ belongs to the edge selection gadget for $i,j$.
\end{claim}
\begin{claimproof}
    We first determine the label of $\{x_1,v_{i,j}^{\star}\}$, where $x_1$ belongs to the edge selection gadget for $i,j$. Note that $x_1$ is connected to the alignment gadget. Let $w\in \hat{W}$ be the vertex of the alignment gadget that is a neighbor of $x_1$. Since $d(w^\star,x_1)=(20n+2)(i+j)$ we have that $\lambda(\{w,x_1\})=(20n+2)(i+j)$.

    First, assume that $\lambda(\{x_1,v_{i,j}^{\star}\})<(20n+2)(i+j)$. Then there is a temporal path from $v_{i,j}^\star$ to $w$ via $x_1$. However, we have that $d(x_{i,j^\star},w)=\infty$, a contradiction.
    Next, assume that $(20n+2)(i+j)<\lambda(\{x_1,v_{i,j}^{\star}\})<n^9+2$. Then there is a temporal path from $w$ to $v_{i,j}$ via $x_1$ with duration strictly less than $n^9-(20n+2)(i+j)+3$. However, we have that $d(w,v_{i,j}^\star)=n^9-(20n+2)(i+j)+3$, a contradiction.
    Finally, assume that $\lambda(\{x_1,v_{i,j}^{\star}\})\ge n^9+2$. Consider a fastest temporal path from $x_1$ to $v_{i,j}^{\star\star}$. This temporal path cannot visit $w$ as its first vertex, since from there it cannot continue. It follows by \cref{claim:2} and the just made assumption that the first edge of the temporal path has a label of at least $n^9$. However, by \cref{claim:2,claim:3} we have that all edges incident with $v_{i,j}^{\star\star}$ have a label of at most $n^9+2$. It follows that $d(x_1,v_{i,j}^{\star\star})\le 3$, a contradiction.

    We can conclude that $\lambda(\{x_1,v_{i,j}^{\star}\})=(20n+2)(i+j)$. Now let $1<\ell\le m$. We have that $d(x_1,x_\ell)=2n\cdot (i+j)\cdot(\ell^2-1)+1$ which implies that $\lambda(\{x_\ell,v_{i,j}^{\star}\})\ge (i+j)\cdot (2n\ell^2 +18n+2)$. Assume that $(i+j)\cdot (2n\ell^2 +18n+2) <\lambda(\{x_\ell,v_{i,j}^{\star}\})\le n^9+2$. Then the temporal path from $x_1$ to $x_\ell$ via $v_{i,j}^\star$ is not a fastest temporal path from $x_1$ to $x_\ell$. Again, we have that a fastest temporal path from $x_1$ to $x_\ell$ cannot visit $w$ as its first vertex, since from there it cannot continue. By \cref{claim:2}, all other edges incident with $x_1$ (that is, all different from the one to $v_{i,j}^\star$ and the one to $w$) have a label of at least $n^9$ and at most $n^9+2$. Similarly, by \cref{claim:2} we have that all other edges incident with $x_\ell$ (that is, all different from the one to $v_{i,j}^\star$) have a label of at least $n^9$ and at most $n^9+2$. It follows that any temporal path from $x_1$ to $x_\ell$ that visits $v_{i,j}^\star$ as its first vertex has a duration strictly larger than $2n\cdot (i+j)\cdot(\ell^2-1)+1$. Any temporal path from $x_1$ to $x_\ell$ that visits a vertex different from $v_{i,j}^\star$ as its first vertex has duration of at most $3$. In both cases we have a contradiction. 
    Lastly, assume that $\lambda(\{x_\ell,v_{i,j}^{\star}\})> n^9+2$. Consider a fastest temporal path from $x_\ell$ to $v_{i,j}^{\star\star}$. Now this temporal path has duration at most 3 since by \cref{claim:2} and the just made assumption all edges incident with $x_\ell$ have label at least $n^9$ whereas by \cref{claim:2,claim:3} all edges incident with $v_{i,j}^{\star\star}$ have label at most $n^9+2$, a contradiction. 
\end{claimproof}

\begin{claim}\label{claim:5}
    For all $1\le i<j\le k$ there exist a permutation $\sigma_{i,j}:[m]\rightarrow [m]$ such that for all $\ell\in[m]$ we have that $\lambda(\{u^\ell_{4n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+2)+8n+4$, where $u^\ell_{4n}$ belongs to the edge selection gadget for $i,j$.

@@

    We can conclude that a fastest temporal path from $x_\ell$ to $v_{i,j}^{\star\star}$ has to visit $v_{i,j}^\star$ as its second vertex and $u^{\ell'}_{4n}$ for some $\ell'\in[m]$ as its second last vertex. Recall that in a  temporal path, the difference between the labels of the first and last edge determine its duration (minus one). Hence, we have that $\lambda(\{u^{\ell'}_{4n},v_{i,j}^{\star\star}\})-\lambda(\{x_\ell,v_{i,j}^{\star}\})+1=8n+5$.
    By \cref{claim:4} we have that $\lambda(\{x_\ell,v_{i,j}^{\star}\})=(i+j)\cdot (2n\ell^2+18n +2)$. It follows that $\lambda(\{u^{\ell'}_{4n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\ell^2 +18n+2)+8n+4$. We set $\sigma_{i,j}(\ell')=\ell$.

@@

\begin{claim}\label{claim:6}
    For all $1\le i<j\le k$,  $\ell\in[m]$, and $\ell'\in[4n]$ we have that $\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+2)+2\ell'+2$, where $u^\ell_{\ell'-1}$ and $u^\ell_{\ell'}$ belong to the edge selection gadget for $i,j$ and $\sigma_{i,j}$ is the permutation of color combination $i,j$.
\end{claim}
\begin{claimproof}
    Let $1\le i<j\le k$ and $\ell\in[m]$.
    By \cref{claim:5} we know that a fastest temporal path from $x_{\sigma_{i,j}(\ell)}$ (of the edge selection gadget for $i,j$) to $v_{i,j}^{\star\star}$ visits $v_{i,j}^\star$ as its second vertex, and $u^{\ell}_{4n}$ (of the edge selection gadget for $i,j$) as its second last vertex. 
    Furthermore, by \cref{claim:4} we have that $\lambda(\{x_{\sigma_{i,j}(\ell)},v_{i,j}^{\star}\})=(i+j)\cdot (2n\cdot {(\sigma_{i,j}(\ell))^2}+18n +2)$ and by \cref{claim:5} we have that $\lambda(\{u^\ell_{4n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2+18n +2)+8n+4$. It follows that there exist a temporal path $P$ from $v_{i,j}^\star$ to $u^\ell_{4n}$ that starts at $v_{i,j}^\star$ later than $(i+j)\cdot (2n\cdot {(\sigma_{i,j}(\ell))^2} +18n+2)$ and arrives at $u^\ell_{4n}$ earlier than $(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+2)+8n+4$. Hence, the temporal path $P$ has duration at most $8n+3$.

@@

    We can conclude that $v^i_j$ can reach a vertex $u^\ell_{\ell'}$ of the edge selection gadget for $i,j+1$ (or $j+1,i$) and a vertex $u^{\ell'}_{\ell'''}$ of the edge selection gadget for color combination $i,j$ (or $j,i$), each along paths of length at least $5n$. From $u^\ell_{\ell'}$ and $u^{\ell'}_{\ell'''}$ we have that any other vertex of the edge selection gadget for $i,j+1$ (or $j+1,i$) and the edge selection gadget for color combination $i,j$ (or $j,i$), respectively, can be reached by a path of length at most $3n$. Together with the observation made in the beginning of the proof, we can conclude that $v^i_j$ can potentially reach any vertex in $\{v^i_{j-1},v^i_j,v^i_{j+1},v^j_{i-1},v^j_i,v^{j+1}_{i-1},v^{j+1}_i\}$ by a path that visits at most $13n$ vertices.

>>>>

Graph realization problems are fundamental graph-algorithmic questions where the objective is to (re)construct a graph, 
given some constraints on some of its graph attributes. Among the most well studied such parameters for graph reconstruction 
are the vertex degrees~\cite{cai2000solution,rfgh611961hu,hakimi1962realizability,barNoy2019graphRealizations,barNoy2021selected}, distances~\cite{barNoy2022GraphRealization,barNoy2021composed,hakimi1965distance}, eccentricities~\cite{barNoy2020efficiently,hell2009linear}, connectivity~\cite{fulkerson1960zero,frank1992augmenting,chen1966realization,erdos1960graphs}, etc. 
The motivation for network realization problems stems from both ``verification'' applications where we attempt to reconstruct an existing network of unknown structure based on the outcomes of experimental measurements, and engineering applications related to network design~\cite{augustine2022distributed}.

@@

Let $G=(V,E)$ and $\Delta\in \mathbb{N}$, and let $\lambda: E \rightarrow \{1,2,\ldots,\Delta\}$ be an edge-labeling function that assigns to every edge of $G$ one of the labels from $\{1,\ldots,\Delta\}$. 
Then we denote by $(G,\lambda,\Delta)$ the \emph{$\Delta$-periodic temporal graph} $(G,\lambda_{\Delta})$, where for every edge $e\in E$ we have $\lambda_{\Delta}(e)=\{i\Delta + x : i\geq 0, x\in \lambda(e)\}$. 
In this case we call $\lambda$ a \emph{$\Delta$-periodic labeling} of $G$.
When it is clear from the context, we drop $\Delta$ form the notation and say that $(G,\lambda)$ is a $\Delta$-periodic temporal graph.

@@

	When considering the problem of finding shortest paths among vertices, one relies heavily on the optimal substructure of the problem,
	which states that if a shortest path $P$ from vertex $u$ to $v$ traverses the vertex $w$,
	then the shortest path from $u$ to $w$ is a subpath of $P$.
	After studying the problem of fastest temporal paths (\ie temporal paths of smallest duration),
	one can see that this property does not carry over
	(for an example see~\cref{fig:ftpExample}).
	Which makes all the standard intuition and work with these kind of paths, much harder.

@@

	\draw[red]
	(v1) edge[diredge2] [out=85,in=95,distance=2.1cm] node[pos=0.3,yshift=2,label=above:$P_{u,w}$] {} (v3) ;
\end{tikzpicture}
	\caption{An example of a temporal graph, where the fastest temporal path $P_{u,v}$ (in blue) from $u$ to $v$ is of duration $7$,
		while the fastest temporal path $P_{u,w}$ (in red) from $u$ to a vertex $w$, that is on a path $P_{u,v}$, is of duration $1$ and is not a subpath of $P_{u,v}$.		
		\label{fig:ftpExample}}
	\end{figure}

@@

    \subparagraph{Verification Gadget.} For each color $i$, we introduce the following vertices. What we describe in the following will be used as a \emph{verification gadget for color $i$}.
    \begin{itemize}
        \item We have one vertex $y^i$ and $k+1$ vertices $v^i_\ell$ for $0\le \ell\le k$.
        \item For every $\ell\in[m]$ and every $j\in[k]\setminus\{i\}$ we have $5n$ vertices $a^{i,j,\ell}_1,a^{i,j,\ell}_2,\ldots,a^{i,j,\ell}_{5n}$ and $5n$ vertices $b^{i,j,\ell}_1,b^{i,j,\ell}_2,\ldots,b^{i,j,\ell}_{5n}$.
        \item We have a set $\hat{U}_i$ of $13n+1$ vertices $\hat{u}^i_1,\hat{u}^i_2,\ldots,\hat{u}^i_{13n+1}$.
    \end{itemize}
    We add the following edges. We add edge $\{y^i,v^i_0\}$.
    %For every $j\in[k]\setminus\{i,i+1\}$ and every $\ell\in[m]$ we add edge $\{v^i_{j-1},\hat{u}^{i,j,\ell}_1\}$. For every $\ell\in[m]$ we add edge $\{\hat{u}^i_{n+3},\hat{u}^{i,i+1,\ell}_1\}$.
    For every $\ell\in[m]$, every $j\in[k]\setminus\{i\}$, and every $\ell'\in[5n-1]$ we add edge $\{a^{i,j,\ell}_{\ell'},a^{i,j,\ell}_{\ell'+1}\}$ and we add edge $\{b^{i,j,\ell}_{\ell'},b^{i,j,\ell}_{\ell'+1}\}$.
    %Assume $1\neq i \neq k$. We describe the two cases $i=1$ and $i=k$ afterwards. 
    %If $i\neq 1$, let $e_\ell\in F_{1,i}$ let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$. Then we add edge $\{v^i_0,u^\ell_{\ell'}\}$ between $v^i_0$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget of color combination $1,i$.

@@

    We add edge $\{v^i_{i-1},\hat{u}^i_1\}$ and for all $\ell\in[13n]$ we add edge $\{\hat{u}^i_\ell,\hat{u}^i_{\ell+1}\}$. Furthermore, we add edge $\{\hat{u}^i_{13n+1},v^i_i\}$. 
    %Let $e_\ell^{i,i+1}\in F_{i,i+1}$ and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell^{i,i+1}$. If $i\neq 1\neq k$, then we add edge $\{\hat{u}^i_{n+3},a^{i,i+1,\ell}_{1}\}$ and edge $\{a^{i,i+1,\ell}_{5n},u^\ell_{n+\ell'-1}\}$ between $a^{i,i+1,\ell}_{5n}$ and the vertex $u^\ell_{n+\ell'-1}$ of the edge selection gadget of color combination $i,i+1$. If $i=1$, then we add edge $\{v^i_0,a^{i,i+1,\ell}_{1}\}$ and edge $\{a^{i,i+1,\ell}_{5n},u^\ell_{n+\ell'-1}\}$ between $a^{i,i+1,\ell}_{5n}$ and the vertex $u^\ell_{n+\ell'-1}$ of the edge selection gadget of color combination $i,i+1$.
%Furthermore, we add edge $\{v_{i+1}^i,b^{i,i+1,\ell}_{1}\}$ and edge $\{b^{i,i+1,\ell}_{5n},u^\ell_{\ell'}\}$ between $b^{i,i+1,\ell}_{5n}$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget of color combination $i,i+1$.

@@

Next, consider the validation gadget for color $i$. 
%Let $1\le j<i$, let $e_\ell\in F_{j,i}$, and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$. We set the following.
%\begin{itemize}
    %\item We set $d(v^i_{j-1},w^i_{\ell'+1})=3$.
    %\item We set $d(w^i_{\ell'},v^i_{j})=3$.
%\end{itemize}
%
For all $0\le j<j'<i$ and all $i\le j<j'\le k$ we set the following.
\begin{itemize}
    \item We set $d(v^i_j,v^i_{j'})=(20n+6)(j'-j)-1$.
\end{itemize}
%The next cases are only relevant if $1\neq i \neq k$. 
%For all $0\le j<i$ %and $\ell\in[n+3]$ we set the following.
%\begin{itemize}
%    \item We set $d(v^i_j,\hat{u}^i_{n+3})=(20n+6)(i-j-1)+2n+5$.
%\end{itemize}
%For all $\ell,\ell'\in[n+3]$ with $\ell<\ell'$ we set the following.
%\begin{itemize}
%    \item We set $d(\hat{u}^i_{\ell},\hat{u}^i_{\ell'})=2(\ell'-\ell)-1$.
%\end{itemize}
For all $0\le j<i$ and all $i\le j'\le k$ we set the following.
\begin{itemize}
    \item We set $d(v^i_j,v^i_{j'})=(20n+6)(j'-j)+6n-1$.
\end{itemize}
%For all 
%$\ell\in[n+3]$ and 
%$i<j\le k$ we set the following.
%\begin{itemize}
%    \item We set $d(\hat{u}^i_{n+3},v^i_j)=(20n+6)(j-i)-1$.
%\end{itemize}

Finally, we consider the alignment gadget. Let $x_1$ belong to the edge selection gadget of color combination $i,j$ and let $w\in \hat{W}$ denote the neighbor of $x_1$ in the alignment gadget. Let $\hat{v}_1$ and $\hat{v}_2$ belong to the first connector gadget of the edge selection gadget for color combination $i,j$. Let $\hat{V}$ contain all vertices $\hat{v}_1$ and $\hat{v}_2$ belonging to the other connector gadgets (different from the first one of the edge selection gadget for color combination $i,j$). 
\begin{itemize}
    \item We set $d(w^\star,x_1)=(20n+6)(i+j)$.
    \item We set $d(w^\star,\hat{v}_1)=n^9$, $d(w,\hat{v}_2)=n^9$, $d(w,\hat{v}_1)=n^9-(20n+6)(i+j)+1$, and $d(w,\hat{v}_2)=n^9-(20n+6)(i+j)+1$.
    \item For each vertex $v\in (V^\star\cup \hat{V})\setminus (X_{i,j}\cup \{v_{i,j}^{\star\star}\})$ we set $d(w^\star,v)=n^9+2$ and $d(w,v)=n^9-(20n+6)(i+j)+3$.
\end{itemize}

@@

\begin{claim}\label{claim:4}
    For all $1\le i<j\le k$ and $\ell\in[m]$ we have that $\lambda(\{x_\ell,v_{i,j}^{\star}\})=(i+j)\cdot (2n\ell^2 +18n+6)$, where $x_\ell$ belongs to the edge selection gadget for $i,j$.
\end{claim}
\begin{claimproof}
    We first determine the label of $\{x_1,v_{i,j}^{\star}\}$, where $x_1$ belongs to the edge selection gadget for $i,j$. Note that $x_1$ is connected to the alignment gadget. Let $w\in \hat{W}$ be the vertex of the alignment gadget that is a neighbor of $x_1$. Since $d(w^\star,x_1)=(20n+6)(i+j)$ we have that $\lambda(\{w,x_1\})=(20n+6)(i+j)$.

    First, assume that $\lambda(\{x_1,v_{i,j}^{\star}\})<(20n+6)(i+j)$. Then there is a temporal path from $v_{i,j}^\star$ to $w$ via $x_1$. However, we have that $d(x_{i,j^\star},w)=\infty$, a contradiction.
    Next, assume that $(20n+6)(i+j)<\lambda(\{x_1,v_{i,j}^{\star}\})<n^9+2$. Then there is a temporal path from $w$ to $v_{i,j}$ via $x_1$ with duration strictly less than $n^9-(20n+6)(i+j)+3$. However, we have that $d(w,v_{i,j}^\star)=n^9-(20n+6)(i+j)+3$, a contradiction.
    Finally, assume that $\lambda(\{x_1,v_{i,j}^{\star}\})\ge n^9+2$. Consider a fastest temporal path from $x_1$ to $v_{i,j}^{\star\star}$. This temporal path cannot visit $w$ as its first vertex, since from there it cannot continue. It follows by \cref{claim:2} and the just made assumption that the first edge of the temporal path has a label of at least $n^9$. However, by \cref{claim:2,claim:3} we have that all edges incident with $v_{i,j}^{\star\star}$ have a label of at most $n^9+2$. It follows that $d(x_1,v_{i,j}^{\star\star})\le 3$, a contradiction.

    We can conclude that $\lambda(\{x_1,v_{i,j}^{\star}\})=(20n+6)(i+j)$. Now let $1<\ell\le m$. We have that $d(x_1,x_\ell)=2n\cdot (i+j)\cdot(\ell^2-1)+1$ which implies that $\lambda(\{x_\ell,v_{i,j}^{\star}\})\ge (i+j)\cdot (2n\ell^2 +18n+6)$. Assume that $(i+j)\cdot (2n\ell^2 +18n+6) <\lambda(\{x_\ell,v_{i,j}^{\star}\})\le n^9+2$. Then the temporal path from $x_1$ to $x_\ell$ via $v_{i,j}^\star$ is not a fastest temporal path from $x_1$ to $x_\ell$. Again, we have that a fastest temporal path from $x_1$ to $x_\ell$ cannot visit $w$ as its first vertex, since from there it cannot continue. By \cref{claim:2}, all other edges incident with $x_1$ (that is, all different from the one to $v_{i,j}^\star$ and the one to $w$) have a label of at least $n^9$ and at most $n^9+2$. Similarly, by \cref{claim:2} we have that all other edges incident with $x_\ell$ (that is, all different from the one to $v_{i,j}^\star$) have a label of at least $n^9$ and at most $n^9+2$. It follows that any temporal path from $x_1$ to $x_\ell$ that visits $v_{i,j}^\star$ as its first vertex has a duration strictly larger than $2n\cdot (i+j)\cdot(\ell^2-1)+1$. Any temporal path from $x_1$ to $x_\ell$ that visits a vertex different from $v_{i,j}^\star$ as its first vertex has duration of at most $3$. In both cases we have a contradiction. 
    Lastly, assume that $\lambda(\{x_\ell,v_{i,j}^{\star}\})> n^9+2$. Consider a fastest temporal path from $x_\ell$ to $v_{i,j}^{\star\star}$. Now this temporal path has duration at most 3 since by \cref{claim:2} and the just made assumption all edges incident with $x_\ell$ have label at least $n^9$ whereas by \cref{claim:2,claim:3} all edges incident with $v_{i,j}^{\star\star}$ have label at most $n^9+2$, a contradiction. 
\end{claimproof}

\begin{claim}\label{claim:5}
    For all $1\le i<j\le k$ there exist a permutation $\sigma_{i,j}:[m]\rightarrow [m]$ such that for all $\ell\in[m]$ we have that $\lambda(\{u^\ell_{4n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+6)+8n+4$, where $u^\ell_{4n}$ belongs to the edge selection gadget for $i,j$.

@@

    We can conclude that a fastest temporal path from $x_\ell$ to $v_{i,j}^{\star\star}$ has to visit $v_{i,j}^\star$ as its second vertex and $u^{\ell'}_{4n}$ for some $\ell'\in[m]$ as its second last vertex. Recall that in a  temporal path, the difference between the labels of the first and last edge determine its duration (minus one). Hence, we have that $\lambda(\{u^{\ell'}_{4n},v_{i,j}^{\star\star}\})-\lambda(\{x_\ell,v_{i,j}^{\star}\})+1=8n+5$.
    By \cref{claim:4} we have that $\lambda(\{x_\ell,v_{i,j}^{\star}\})=(i+j)\cdot (2n\ell^2+18n +2)$. It follows that $\lambda(\{u^{\ell'}_{4n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\ell^2 +18n+6)+8n+4$. We set $\sigma_{i,j}(\ell')=\ell$.

@@

\begin{claim}\label{claim:6}
    For all $1\le i<j\le k$,  $\ell\in[m]$, and $\ell'\in[4n]$ we have that $\lambda(\{u^\ell_{\ell'-1},u^\ell_{\ell'}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+6)+2\ell'+2$, where $u^\ell_{\ell'-1}$ and $u^\ell_{\ell'}$ belong to the edge selection gadget for $i,j$ and $\sigma_{i,j}$ is the permutation of color combination $i,j$.
\end{claim}
\begin{claimproof}
    Let $1\le i<j\le k$ and $\ell\in[m]$.
    By \cref{claim:5} we know that a fastest temporal path from $x_{\sigma_{i,j}(\ell)}$ (of the edge selection gadget for $i,j$) to $v_{i,j}^{\star\star}$ visits $v_{i,j}^\star$ as its second vertex, and $u^{\ell}_{4n}$ (of the edge selection gadget for $i,j$) as its second last vertex. 
    Furthermore, by \cref{claim:4} we have that $\lambda(\{x_{\sigma_{i,j}(\ell)},v_{i,j}^{\star}\})=(i+j)\cdot (2n\cdot {(\sigma_{i,j}(\ell))^2}+18n +2)$ and by \cref{claim:5} we have that $\lambda(\{u^\ell_{4n},v_{i,j}^{\star\star}\})=(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2+18n +2)+8n+4$. It follows that there exist a temporal path $P$ from $v_{i,j}^\star$ to $u^\ell_{4n}$ that starts at $v_{i,j}^\star$ later than $(i+j)\cdot (2n\cdot {(\sigma_{i,j}(\ell))^2} +18n+6)$ and arrives at $u^\ell_{4n}$ earlier than $(i+j)\cdot (2n\cdot (\sigma_{i,j}(\ell))^2 +18n+6)+8n+4$. Hence, the temporal path $P$ has duration at most $8n+3$.

@@

    We can conclude that $v^i_j$ can reach a vertex $u^\ell_{\ell'}$ of the edge selection gadget for $i,j+1$ (or $j+1,i$) and a vertex $u^{\ell'}_{\ell'''}$ of the edge selection gadget for color combination $i,j$ (or $j,i$), each along paths of length at least $5n$. From $u^\ell_{\ell'}$ and $u^{\ell'}_{\ell'''}$ we have that any other vertex of the edge selection gadget for $i,j+1$ (or $j+1,i$) and the edge selection gadget for color combination $i,j$ (or $j,i$), respectively, can be reached by a path of length at most $3n$. Together with the observation made in the beginning of the proof, we can conclude that $v^i_j$ can potentially reach any vertex in $\{v^i_{j-1},v^i_j,v^i_{j+1},v^j_{i-1},v^j_i,v^{j+1}_{i-1},v^{j+1}_i\}$ by a path that visits at most $13n+1$ vertices.
